%Description - Contains A description of how to make to script files battle each other, 

\section{ Description of WAR }
\label{sec:describeWAR}
WAR is a basic scripting language, enabling scriptwriters to script out battles, and let them carry out on their own without them. The winner of the simulation will be the one with the best script. \\
	\subsection{The simulation}
		To run a simulation in the WAR simulator a configuration file and at least two team files has to be fed to the simulation engine. 
		These files are written in the WAR scripting language.
		\\
		The configuration file is used to establish basic rules for the war simulation, i.e. the size of the battlefield, the maximal values of properties and the standard properties of regiments.
		The thought behind this, is to allow for some flexibility in altering the simulation from game to game.
		Each participant will make a script file over their team of regiments, which will be provided to the simulator, 
		which then will interpret the script and simulate the battle. 
		These script files contain how many units and what kind of units the participant would like to use. 
		They may also contain information regarding the behaviour of specific regiments. 
		\\
		The one who makes the best script will win the game, so every participant should strive to make the best script, 
		and place their regiments in the best locations on the grid.
		\\
		When both players are coding their scripts, they will provide the script-files with information about their regiments, 
		but if the player chooses to leave the information out, or even forgets to specify it, 
		the simulator will assign a default value - given by the standard values found in the configuration file. 
		This helps both rookie scriptwriters and forgetful scriptwriters to provide the simulator 
		with the amount of information required to initiate the simulation.

	\subsection{The language}
		The WAR language will be a simple imperative scripting language. 
		We want the language to be easy to program, so inexperienced programmers will be able to make a simulation, which is why we chose to
		make the language very simple. The imperative paradigm is what we felt best supported the idea of a simple programming language. We don't need the
		powerful abstractions of object orientated programming nor the task-solving capabilities of the functional languages. At the same time, the language should provide enough support, that more experienced programmers have an advantage over inexperienced programmers - the winner should be determined by their scripting skills.
		
		 
	\subsection{Definition of the terms in WAR}
	In this section we will define the different terms of the simulation and of the terms seen in the configuration- and team file.
	
		\subsubsection{Terms of the simulation}
		
		\subsubsection{Team}		
		A team consists of 1 or more regiments. In the simulation two or more teams will battle to win the simulation. A team is synonymous to an army.
		
		\subsubsection{Turn}
		Each of the regiment will have a turn each round where they can perform a limited number of actions. The number of actions allowed per regiment per turn, is defined in the simulator.
		The turn will end if the regiment is out of action or if the regiment doesn't want to perform any Actions. 
		The actions performed by a regiment is predefined in the behaviour. 
		Further description of events during a turn, will be described in the following section.
		
		\subsubsection{Round}
		A simulation consists of 1 or more rounds. When a round begins each regiment will be given a turn.
		The teams take turns performing the behaviour of their regiments. 
		A new round will start when every regiment have used their turns.
		Further description of rounds are found in the following section.

		\subsubsection{Behaviour}
		Behaviour allows the scriptwriters to define how each regiment behaves. 
		By using control statements, the scriptwriter may make the regiment behave in a defensive or offensive way, 
		using the provided methods in the language. As an example you may instruct a ranged regiment to behave in such a way, 
		as to not approach another regiment, and only open fire if that regiment is within the range of your archer regiment.
				
		\subsubsection{Grid}
		The grid is a 2 dimensional map where the teams will battle.
		The grid, might be seen as a map, table, or battlefield where the 'battle' will take place. 
%		Each 'Grid' will have a name, and certain properties which \textbf{must} be defined in the configuration file.
																		
		\subsubsection{Terms in the team file }
	
		\subsubsection{Size}
		The size of the regiment is, in abstraction, the number of soldiers in the current regiment. 
		The size is closely connected with the total health of the regiment, as well as total damage done by the regiment.
		The size also provides information about how much space the regiment takes up on the grid. A regiment off size $200$ would take up $200$ grid tiles.
%		One might consider it as the overall health of the regiment. While size may be an abstraction of health,
%		it's important to notice that a regiment with a larger size takes up more integers on the grid.

		\subsubsection{Health}
		Health describes the initial health of each unit in the regiment.
		
		\subsubsection{Type}
		The Type defines how a regiment attacks. A regiments Type can only be Melee or Ranged.
		Melee regiments can only attack regiments adjacent to their position, while ranged regiments 
		can attack any regiment within their specified range.
		
		\subsubsection{Range}
		Range defines how far a regiment of Type Ranged can attack. 
		If a Range is defined for a regiment of type Melee, this is simply ignored.
		
		\subsubsection{Damage}
		The damage of a regiment is an abstraction of the damage done by each unit in the regiment. 
		
		\subsubsection{Movement}
		Movement defines how many tiles a regiment is allowed to move.
		
		\subsubsection{Attackspeed}
		Attackspeed governs how many attacks are performed by regiment each turn, giving units further interesting properties. 
		However, in the context of the simulation, the attackspeed is quite simply a multiplier of the damage done by the regiment.
		
		\subsubsection{Actions}
		When a regiment has its turn they are allowed to do some actions, Attack, MoveTowards or MoveAway. \\
		For describing these action we set a precondition(what is required to do the action), a failure(what happens if the condition isn't met)
		and result(what happens if the condition is met).
		
		\subsubsection{Attack action}
		Usage: \\
		Attack(Regiment) \\
		
		Precondition: \\
		The regiment has its turn. \\
		For a regiment of attacktype ranged the regiment must be in range. \\
		For a regiment of attacktype melee the enemy regiment must be 1 tile away(diagonals included). \\
		The Regiment must be eligible to perform additional actions in this turn.\\
		
		Failure: \\
		Nothing happens \\
		
		Result: \\
		The enemy regiment current total health pool is calculated.\\ 
		The total damage of the attacking regiment is calculated. \\
		The damage is subtracted from the total health pool of the enemy regiment.\\
		The enemy regiments size is reduced by a number corresponding to the number of units that would die, in correspondence to the damage taken.\\
		
		\subsubsection{MoveTowards action}
		Usage: \\
		MoveTowards(Regiment) \\
		
		Precondition: \\
		The regiment has its turn, the given regiment exists and the tiles (left,right,up down) 
		which brings the regiment towards the target regiment isn't blocked.\\
		The Regiment must be eligible to perform additional actions in this turn.\\
		
		Failure: \\
		Nothing happens \\
		
		Result: \\
		The regiment will move a number of tiles equal to its movement, in the direction of the specified regiment.
		%The regiment will move 1 tile (left,right,up down) towards the friendly/enemy regiment and movement is decreased by 1.
		
		\subsubsection{MoveAway action}
		Usage: \\
		MoveAway(Regiment) \\
		
		Precondition: \\
		The regiment has its turn, the given regiment exists and the tiles (left,right,up down) 
		which brings the regiment towards the target regiment isn't blocked.
		
		Failure: \\
		Nothing happens \\
		
		Result: \\
		The regiment will move a number of tiles equal to its movement, in the opposite direction of the specified regiment.
		%The regiment will move 1 tile (left,right,up down) towards the friendly/enemy regiment and movement is decreased by 1.
				
		\subsubsection{Terms in the configuration file}
%		The simulation will need basic instructions which is a common limitation of both teams, to ensure even 'armies'. 
%		As mentioned earlier this is defined in a configuration file.
		
		\subsubsection{Width}
		Width defines the width of the grid measured in tiles.
		
		\subsubsection{Height}
		Height defines the height of the grid measures in tiles.
		
		\subsubsection{Standards block}
		This block will contain standard properties for regiments. These will be used if the necessary 
		information for a regiment is not entered in the main script, the regiment will use these standard properties.
		
		\subsubsection{Maxima block}
		This block sets the limitations for the properties of the regiments. E.g. regiments must be of size 200 or less.

\section{ Running a simulation }
%Dette skal måske ikke være her. Hvis det flyttes, så vær opmærksom på referencerne i ovenstående section, under Round og Turn
	When the simulation engine has been provided with a configuration file and two or more team files, the simulation will run. During a simulation, alot of things happen, that are not defined in the WAR code. This section will explore these events and provide some insight in what happens during a simulation.
		\subsubsection{Beginning the simulation}
		When beginning the simulation, the configuration file and all provided team files are read and interpreted. The information found in these files is used by the simulator during the simulation. When the files have been interpreted, the simulation starts by picking a team at random. The chosen team is the first to evaluate its regiments turns. If there are more than two teams, the next team to go, is also chosen at random. The sequence of the teams will be consistent throughout the rounds of the simulation. All teams are added to a list of playing teams. Only teams on this list can participate in a round. When a team is initialized, each regiment related to the team, is stored in list, private to the team. This list contains all regiments, that are eligible to perform actions in a turn. 
		\subsubsection{The events of a Teams round}
		At the beginning of a teams round, the simulation engine checks if the team is still eligible to play. To be eligible, the team must still have "living" regiments. A regiment is considered living, if there is at least 1 unit left in the regiment - i.e. the regiments size must be at least 1. If the team is not eligible to play, it is removed from the list of playing teams. If there is only one team left on the list, and that team is eligible to play, that team wins the simulation. If the team is eligible to play, the simulation engine begins iterating through the regiments of the teams, performing the actions deciphered from the behaviour in the script files. Each regiments behaviour is performed in the regiments own turn - no regiment actions are performed in parallel.
		\subsection{The events of a regiments turn}
		A Regiment can only take a turn, if the regiment exists on the team-specific list of regiments eligible to take turns and the regiment is still considered living. If the regiment is no longer considered living, the regiment is removed from the list. If the regiment is eligible to take a turn, the behaviour of the regiment is performed, according to WAR script, so long as the regiment is still allowed to perform additional actions. If the behaviour contains one of the methods; Attack, MoveTowards, MoveAway, they are performed, as described in section \ref{sec:describeWAR}. If one or more of the three methods are performed, the grid is updated to reflect the change - be it the size of an regiment or the position of a regiment. In addition to the updated grid, the regiment is also allowed one less action for the current turn per method called.