This report is about the project that, was developed in the Spring semester of 2011, by the group D204A at the Department of Computer Science at Aalborg University. The group consisted of students attending their fourth semester of Computer Science. The project was undertaken in cooperation with supervisor Paolo Viappiani. \\
\\
In the report, the reader is assumed to have basic knowledge of programming languages, and a certain insight into the overall structure of the implementation of a programming language and the meaning of compilers and interpreters. The topic of the report is development of a programming language, and thereby the implementation of a interpreter for this language. \\
The language is developed in C$\sharp$ which assumes the reader is familiar with basic object-oriented programming. \\
\\
In addition to the report itself, a disc is included containing the source-code for further examination. \\
In order to run or compile this code a .NET Framework needs to be present and functioning on the machine. \\

The report documents the process of the language design, and details how the language is implemented. In doing so it also describes usage cases, and testing, along with an overall description and images of the application itself. \\

References are cited using the Vancouver method and are found in the bibliography of the report, at the very end. 
Figures and tables are numbered in accordance with Chapter and section numbers throughout the report.
% Further information, or another copy of the source code may be obtained at http://cs.aau.dk/HERPDERP(Placeholder).

\newpage\mbox{}\newpage